---
output: github_document
---

<!-- index.md is generated from index.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# different.tan

<!-- badges: start -->
<!-- badges: end -->

R code for the analysis of vehicle emissions remote sensing systems (VERSS).  

> In development package

## Installation

You can install the development version of different.tan from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("karlropkins/different.tan")
```

## Contributing

**different.tan** is an in-development package, and contributions are very welcome. We are using tidyverse contribution guidance regarding code of conduct but are not strict as them regarding coding style...  [Contributions](https://karlropkins.github.io/different.tan/CONTRIBUTING.html) 

## Examples

Load __different.tan__ package and get some VERSS data, e.g. from the Denver [FEAT Archive](https://digitalcommons.du.edu/feat/):

```{r, message=FALSE, warning=FALSE}
require(different.tan)
feat <- import_featdata("Fresno 21")
```

A quick Pareto analysis:

```{r Pareto, dpi=400} 
plot_Pareto(nox.gkg, fuel, data=feat, Pareto = "cum.Pareto", transpose.y.percent=c(80, 95))
```

Here, for example, we see that 95\% of observed NOx emissions were produced by about 25\% passing cars, and 80\% were produced about 6\% passing cars.
